---
title: ""
---


Please select the provider you would like to consult with. You will be directed to their calendar to choose an available time slot.

---

<div class="card">

## Biraj Bhattarai

<!-- For speech, language, hearing, and neurological communication consultation. -->
> I specialize in acquired neurogenic communication and swallowing disorders.
I help people whose speech, language, or swallowing has been affected by stroke, brain injury, Parkinson's disease, or other neurological conditions.
I work with adults and children with voice disorders, stuttering, and other communication challenges.
With my combined training and research in both speech-language pathology and audiology, I can see the full picture of your communication needs and curate necessary services.

I accept post-acute and chronic-phase referrals for aphasia, motor speech disorders, dysphagia, and AAC.

<a href="https://calendar.app.google/jtq4Jkqq7qGCqcBJ7" target="_blank" class="button">Book with Biraj Bhattarai</a>

</div>

---

<div class="card">

## Dr. Sajana Aryal

<!-- For speech, language, hearing, tinnitus, and communication-related consultation. -->
> I work with adults and children experiencing hearing loss, tinnitus, auditory processing difficulties, and the communication challenges that follow.
With my extended training and research in audiology, I bridge the gap between hearing health and communication rehabilitation,
whether you've just received a audiological diagnosis (such as hearing loss, auditory processing disorder), are struggling with ringing in your ears, or need support navigating life with a hearing device.

<!-- I specialise in audiological rehabilitation and tinnitus management. -->
I accept referrals for audiological and aural rehabilitation, APD, tinnitus management (including, tinnitus retraining therapy), and hearing- and vestibular-related communication intervention.

<a href="https://calendar.app.google/6cVyaYHpytMepqPP8" target="_blank" class="button">Book with Dr. Sajana Aryal</a>

</div>

---

<div class="card">

## Dr. Pratik Bhandari

<!-- For speech, language, cognition, and communication-related consultation. -->
> I work at the intersection of brain science and communication.
If you or a loved one is experiencing changes in memory, attention, reasoning, or social communication, or if you have a complex language profile that hasn't been fully explained, I bring a deeper scientific lens to understanding what's happening and what could help.
I work with conditions like <!-- dementia -->traumatic brain injury, autism (in adults and children), fluency disorders (stuttering), and complex developmental language profiles.

I also work with clients who want a research-informed, evidence-based deep-dive into their communication difficulties when standard assessments have so far been inconclusive.

<a href="https://calendar.app.google/P8WZmZ9YLrHQdWcU8" target="_blank" class="button">Book with Dr. Pratik Bhandari</a>

</div>

---

## BEFORE YOUR APPOINTMENT

Please prepare the following information:

- Main concern or reason for consultation  
- Any previous diagnosis or reports (if available)  
- Speech, language and hearing evaluation test results (if available)  
- Questions/conerns you would like to discuss/share  

---

## IMPORTANT INFORMATION!!

- Sessions are conducted online via Google Meet (Make sure you have good internet access)
- You will receive a confirmation email after booking  
- A meeting link will be shared automatically  

---

<div style="text-align:center;">
  <h1> CONSULTATION FEES </h1>
</div>

```{r setup-fees-data, cache=TRUE, include=FALSE}

library(reactable)
# library(kableExtra)
# library(flextable)

df <- dplyr::tibble(
  Service = c("Initial comprehensive assessment", "Follow-up therapy session", "Caregiver coaching session", "Second opinion consultation"),
  "Duration (approx.)" = c("30-40 minutes", "25-30 minutes", "20-25 minutes", "15-20 minutes"),
  Fees = c("Rs.1600/USD180", "Rs.1000/USD150", "Rs.800/USD110", "Rs.500/USD80")
)

```

```{r, render-table, cache=TRUE, echo=FALSE}
reactable(df)

# kbl(df)
# flextable(df)
```

---

## PAYMENT INFORMATION

You can pay online using the following methods:

<a href="#" style="color:#0B4F6C; text-decoration:none;">Fonepay</a>  
<a href="#" style="color:#0B4F6C; text-decoration:none;">Khalti</a>  
<a href="#" style="color:#0B4F6C; text-decoration:none;">eSewa</a>  

**Note:**  
Payment is required before each consultation after booking an appointment.

---

<div style="text-align:center;">
  <a class="button" href="appointment.html">Book Your Appointment</a>
</div>

 