---
title: ""
---

Please review the consultation charges for each specialist below.

---

### Biraj Bhattarai  
Consultation per session: NRS 1000/ USD 50

### Dr. Sajana Aryal  
Consultation per session: NRS 1000/ USD 50

### Dr. Pratik Bhandari  
Consultation per session: NRS 1000/ USD 50

---

## PAYMENT INFORMATION

You can pay online using the following methods:

<a href="#" style="color:#0B4F6C; text-decoration:none;">Fonepay</a>  
<a href="#" style="color:#0B4F6C; text-decoration:none;">Khalti</a>  
<a href="#" style="color:#0B4F6C; text-decoration:none;">eSewa</a>  

**Note:**  
Payment is required before each consultation after booking an appointment.

---

```{r setup-fees-data, include=FALSE}

library(reactable)
# library(kableExtra)
# library(flextable)

df <- dplyr::tibble(
  Service = c("Initial comprehensive assessment", "Follow-up therapy session", "Caregiver coaching session", "Second opinion consultation"),
  "Duration (approx.)" = c("30-40 minutes", "25-30 minutes", "20-25 minutes", "15-20 minutes"),
  Fees = c("Rs.1600/USD180", "Rs.1000/USD150", "Rs.800/USD110", "Rs.500/USD80")
)

```

```{r, render-table, echo=FALSE}
reactable(df)

# kbl(df)

# flextable(df)
```
